---
title: "Plotly"
---

This page shows some example plotly plots

```{r}
library(tidyverse)
library(viridis)
library(p8105.datasets)

library(plotly)
```

```{r}
set.seed(1)

data(nyc_airbnb)
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(boro = neighbourhood_group, neighbourhood, rating, price, room_type,
         latitude, longitude) %>%
  filter(!is.na(rating), 
         boro == "Manhattan",
         room_type == "Entire home/apt",
         price %in% 100:500)  %>% 
  sample_n(5000)
```

Creating plotly scatterplot

```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, '\nRating: ', rating)) %>% 
  plot_ly(x = ~longitude, y = ~latitude, type = "scatter", mode = "markers",
          alpha = 0.5, 
          color = ~price,
          text = ~text_label)
```

Doesn't matter what order the syntax is inside the bracket once you use plot_ly 

plotly boxplots
 
```{r}
nyc_airbnb %>% 
    plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "Set2")
```
you can isolate different neighbourhoods with the legend
```{r}
common_neighborhoods =
  nyc_airbnb %>% 
  count(neighbourhood, sort = TRUE) %>% 
  top_n(8) %>% 
  select(neighbourhood)
## Selecting by n

inner_join(nyc_airbnb, common_neighborhoods,
             by = "neighbourhood") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box",
          colors = "Set2")
```
innerjoin? 

## Bar plots

Trust me you can make this 

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar")
## Warning in RColorBrewer::brewer.pal(N, "Set2"): n too large, allowed maximum for palette Set2 is 8
## Returning the palette you asked for with that many colors
```

You can convert a ggplot object straight to an interactive graphic using ggplotly.

For example, the code below recreates our scatterplot using ggplot followed by ggplotly.

```{r}
scatter_ggplot = 
  nyc_airbnb %>%
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = 0.25) +
  scale_color_viridis() +
  coord_cartesian() +
  theme_classic()

ggplotly(scatter_ggplot)
```
 first creat the plot as you want as a ggplot and then convert to a plot_ly. Plot_ly takes way more time and on the backend requires more downloads etc. 


